Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-20 Paper2015.tex
Considered page 4's comments.
Updated abstract.

\begin{abstract}
    Monte Carlo simulation of spallation neutron source of ANITA at TSL was used to analyze radiation fields at the Close User Position (CUP) and Standard User Position(SUP) for single-event effect testing. ...
    \todo{Revise abstract}
\end{abstract}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{Standard User Position}
        \label{fig:GammaSpatialDistributionSUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{Close User Position}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{
        Calculated gamma spatial distribution, with
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{Standard User Position}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{Close User Position}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{
        Calculated gamma dose spectra, with
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:GammaDoseEnergy}
\end{figure}

>>>>

\begin{abstract}
    Simulations of the ANITA spallation neutron source at The Svedberg Laboratory (TSL) are described.
    Neutron field calculates show close agreement with measurements at both standard and close user positions.
    Gamma radiation characteristics are also predicted.
\end{abstract}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=0.9\columnwidth]{SUP10ColSpatialDistributionAllG.png}
        \subcaption{Standard User Position}
        \label{fig:GammaSpatialDistributionSUP}
        \todo{Fig~\ref{fig:GammaSpatialDistributionSUP}: consider what to do with this figure.}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=0.9\columnwidth]{CUP10ColSpatialDistributionAllG.png}
        \subcaption{Close User Position}
        \label{fig:GammaSpatialDistributionCUP}
    \end{minipage}
    \caption{
        Calculated gamma spatial distribution, with
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergySUP.eps}
        \subcaption{Standard User Position}
        \label{fig:GammaDoseEnergySUP}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \centering
        \includegraphics[width=0.9\columnwidth]{DoseVSenergyCUP.eps}
        \subcaption{Close User Position}
        \label{fig:GammaDoseEnergyCUP}
    \end{minipage}
    \caption{
        Calculated gamma dose spectra, with
        \SI{10.2}{\cm} diameter collimator
    }
    \label{fig:GammaDoseEnergy}
    \todo{Fig.~\ref{fig:GammaDoseEnergy}: correct y axis units. Consider whether to combine.}
\end{figure}
